---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ssMRCT

<!-- badges: start -->
<!-- badges: end -->

The goal of ssMRCT is to provide a comprehensive suite of functions for designing and analyzing Multi-Regional Clinical Trials (MRCTs) under fixed effects model and random effects model for regulatory decision support and trial optimization in global drug development programs.

## Installation

You can install the development version of ssMRCT from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("kunhaiq/ssMRCT")
```

## Example

This is a basic example which shows you how to solve a common problem.
Suppose the significance level is 0.05 and the desired power is 0.8. 
Additionally, the difference in mean of the clinical trial response is 1 and 
its corresponding variance is 16. We need to compute the minimal overall sample
size and regional sample size, which equals the regional proportion times the 
overall sample size.

```{r example}
library(ssMRCT)
## conProb() gives the consistency probability under fixed effects model
conProb(alpha = 0.05, power = 0.8, rF = 0.271, d = 1, sigmaTrt = 4)
## regFrac() gives the optimal regional fraction under fixed effects model
regFrac(alpha = 0.05, power = 0.8, d = 1, sigmaTrt = 4)
```

Also we could consider to conduct two MRCTs

```{r 2MRCT}
## conProb2() gives the consistency probability under fixed effects model
conProb2(alpha = 0.05, power1 = 0.8, power2 = 0.9, rF1 = 0.141, d1 = 1, sigmaTrt1 = 4) 
## regFrac2() gives the optimal regional fractions under fixed effects model
regFrac2(alpha = 0.05, power1 = 0.8, power2 = 0.9, d1 = 1, sigmaTrt1 = 4)
```

For MRCT under random effects model, one could use

```{r randomEffects}
## ssCPnorm() gives the consistency probability under random effects model
ssCPnorm(alpha=0.025, beta=0.2, delta=0.25, tau=0.1, sigma1r=rep(1,3),
         sigma0r=rep(1,3), randRatio=1, pi=0.5, target=1, f=c(1/3,1/3,1/3))
```
 
